PANCHANGE_data_preprocessing

### 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd
added pcl to ramp

## RAMP - NOT YET HAVE THE RAMP PCL DATA READY
```{r coping ramp pcl cols}
# if(RAMP == TRUE) {
# coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
# dim(coping.ramp.pcl.raw)
# colnames(coping.ramp.pcl.raw)
# }
```

```{r coping ramp pcl summary labels}
# if(RAMP == TRUE) {
# summarytools::dfSummary(
#   coping.ramp.pcl.raw,
#   graph.col = F,
#   valid.col = F,
#   labels.col = F
# )
# }
```

@@

```{r coping ramp pcl cleaning}
# if(RAMP == TRUE) {
# coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
#   drop_na(externalDataReference) %>% # Drop NAs
#   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
#   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
#   mutate(ID = as.numeric(ID)) %>%
#   select(
#     Sample, # Sample
#     ID, # ID
#     pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
#     pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
#     pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
#     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
#     pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
#     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
#     pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
#     pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
#     pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
#     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
#     pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
#     pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
#   ) %>%
#   add_numeric(., exclude = exclude_cols) %>%
#   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
#   mutate_if(is.numeric, ~na_if(., -99)) %>%
#   mutate_if(is.numeric, ~na_if(., -77)) %>%
#   mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
#   mutate_if(is.factor, ~na_if(., "Don't know")) %>%
#   mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
#   mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
# 
# # Inspect dimensions
# dim(coping.ramp.pcl.raw.id)
# # Inspect colnames
# colnames(coping.ramp.pcl.raw.id)
# #Differences
# dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
# }
```

```{r coping ramp pcl copy}
# if(RAMP == TRUE) {
#   coping.pcl.raw.id <- coping.ramp.pcl.raw.id
# }
```

@@

Removing all prepandemic dataframes from NBR/RAMP (prepandemic measures don't exist for these cohorts)
```{r nbr/ramp data frame list}
if(NBR == TRUE | RAMP == TRUE) {
dfs.list <- list(
  dem.raw.id,
  mhd.raw.categories,
  coping.gad.raw.id,
#  coping.pcl.raw.id, #WAITING FOR PCL DATA FOR RAMP
  coping.phq.raw.id,
  coping.ocir.raw.id
)
}
```

>>>>

## RAMP - NOT YET HAVE THE RAMP PCL DATA READY
```{r coping ramp pcl cols}
if(RAMP == TRUE) {
coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
dim(coping.ramp.pcl.raw)
colnames(coping.ramp.pcl.raw)
}
```

```{r coping ramp pcl summary labels}
if(RAMP == TRUE) {
summarytools::dfSummary(
  coping.ramp.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = T
)
}
```

@@

```{r coping ramp pcl cleaning}
if(RAMP == TRUE) {
coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_reminded_upset, # differ to RAMP prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.stressful_experience_avoiding_activities, # differ to RAMP prepan
    pcl.cut_people_feeling_distant_base = pcl.feeling_distant_cut_people, # differ
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_reminded_upset.1, # differ
    pcl.stressful_situation_avoiding_activities_retro = pcl.stressful_experience_avoiding_activities.1, # differ
    pcl.cut_people_feeling_distant_retro = pcl.feeling_distant_cut_people.1, # differ
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.ramp.pcl.raw.id)
# Inspect colnames
colnames(coping.ramp.pcl.raw.id)
#Differences
dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
}
```

```{r coping ramp pcl copy}
if(RAMP == TRUE) {
  coping.pcl.raw.id <- coping.ramp.pcl.raw.id
}
```

@@

Removing all prepandemic dataframes from NBR/RAMP (prepandemic measures don't exist for these cohorts)
```{r nbr/ramp data frame list}
if(NBR == TRUE | RAMP == TRUE) {
dfs.list <- list(
  dem.raw.id,
  mhd.raw.categories,
  coping.gad.raw.id,
  coping.pcl.raw.id,
  coping.phq.raw.id,
  coping.ocir.raw.id
)
}
```
